A quantum parallel Markov chain Monte Carlo

### 2021-11-29 main.tex
statement of purpose

\emph{In the presence of these trade-offs, we seek to enjoy the benefits of parallel MCMC while (\textcolor{red}{a}) limiting the total amount of computing necessary and (\textcolor{red}{b})  retaining conventional parallel computing resources for secondary computational bottlenecks such as proposal generations and proposal density evaluations. Here, we assert that established quantum algorithms can help achieve these twin goals.}

@@

\section{Bare-bones quantum computing}\label{sec:shortIntro}

>>>>

\emph{In the presence of these trade-offs, it is worthwhile to develop additional parallel computing tools for parallel MCMC so that future scientists may be better able to flexibly assign sub-routines to different computing resources in a way that is tailored to their specific inference task.  In particular, we show that quantum parallelization can be a useful tool for parallel MCMC when evaluation of the target density represents the computational bottleneck.}

%\emph{In the presence of these trade-offs, we seek to enjoy the benefits of parallel MCMC while (\textcolor{red}{a}) limiting the total amount of computing necessary and (\textcolor{red}{b})  retaining conventional parallel computing resources for secondary computational bottlenecks such as proposal generations and proposal density evaluations. Here, we assert that established quantum algorithms can help achieve these twin goals.}

@@

\section{Limited introduction to quantum computing}\label{sec:shortIntro}
